Uncovering underlying high-level musical content in the temporal domain \\ \small Leveraging deep learning, inductive bias, and aural music skills to learn embedding spaces from raw waveforms with applications to MIR downstream tasks

### 2023-05-10 introduction/Subsections/Assumptions.tex
Updates from Overleaf

Abstract features, such as melody, harmony, rhythm, tempo, form, and expression, can be identified irrespective of waveform or production style. This approach offers an objective and comprehensive insight into a piece's musical content and meaning, analogous to how analyzing sheet music unveils a composition's underlying structure and intent.

>>>>

Abstract high-level features, such as melody, harmony, rhythm, tempo, form, and expression, can be identified irrespective of waveform or production style. This approach offers objective and comprehensive insight into a piece's musical content and meaning, analogous to how analyzing sheet music unveils a composition's underlying structure and intent.
